Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
a  few more

Looking at equivalent properties, we foun overall little overlap among records; that is, except for the smallest records (which had few properties to begin with), most of the data records had more unique properties than ones in common with others.  While some of these 'unique records' were primarily for internal, service-specific use (such as service-specific IDs) others were useful properties one would expect to find in a record that were simply not present.  Only one of the music data providers, Spotify, included information about the album(s) that featured a particular song.  Such omissions show us that these data APIs reflect each service provider's own capabilities and internal data representations very specifically, and that integrating data such records from multiple sources could allow more complete and useful representations to be assembled.

The second finding is that equivalent properties were sometimes, though only rarely, given the same name.  Thus, terminological heterogeneity was prevalent across data records we observed.  Structural heterogeneity, however, was comparatively rare, with the most common case being similar to the birthday example above; a leaf property on one record modeled as a subtree in the other.  We also encountered, particularly in the Weather category, examples of fields which had data embedded in textual description fields, which hints their intended use in RSS and other feed readers than as stuctured data feeds.

Modelling heterogeneity was also comparatively rare,

>>>>

Looking at equivalent properties, we foun overall little overlap among records; that is, except for the smallest records (which had few properties to begin with), most of the data records had more unique properties than ones in common with others.  While some of these 'unique records' were primarily for internal, service-specific use (such as service-specific IDs) others were useful properties that were simply not present.  Only one of the music data providers, Spotify, included information about the album(s) that featured a particular song.  Such omissions show us that these data APIs reflect each service provider's own capabilities and internal data representations very specifically, and that integrating data such records from multiple sources could allow more complete and useful representations to be assembled.

The second finding is that equivalent properties were sometimes, though only rarely, given the same name.  Thus, terminological heterogeneity was prevalent across data records we observed.  Structural heterogeneity, however, was comparatively rare, with the most common case being similar to the birthday example above; a leaf property on one record modeled as a subtree in the other.  We also encountered, particularly in the Weather category, examples of fields which had data nested in textual description fields, which hints their intended use in RSS and other feed readers than as stuctured data feeds.

Examples of modelling/semantic heterogeneity instances were rarer than those of structural heterogeneity, with the few we found mostly being attributed to concepts on one site not mapping perfectly to those of another site; ``Promotions'' versus ``Offers'',
